Improved Bounds for Online Balanced Repartitioning

### 2020-04-22 paper/disc20clustering.tex
Generic algorithm rewrite

\begin{theorem}
  \TAlg is $O(\ell)$-competitive.
  \maciek{Let Reconf(k,l) be a bound on the cost of the reconfiguration. Then \TAlg is $O(Reconf(k,l)\cdot k \cdot \ell)$-competitive.}
\end{theorem}
\begin{proof}
  Fix a completed phase, and consider the state of \TAlg's counters at the end of it.
  We consider the incomplete phase later in this proof.

@@

@@

\maciek{Intro: compare to previous algorithm. Note strict competitive ratio vs large additive term.}

>>>>

\begin{theorem}
  \TAlg is $O(\ell)$-competitive.
  \maciek{Proposed new formulation (current version is all about k=3 still): Let Reconf(k,l) be a bound on the cost of a single reconfiguration. Then \TAlg is $O(Reconf(k,l)\cdot k \cdot \ell)$-competitive.}
\end{theorem}
\begin{proof}
  Fix a completed phase, and consider the state of \TAlg's counters at the end of it.
  We consider the incomplete phase later in this proof.

@@

Corollary: DET2 is $O(\ell)$-competitive for $k=3$.

@@

\maciek{Intro: compare to previous 7-competitive algorithm. Note strict competitive ratio vs large additive term. Also, emphasize that in this section the algorithm is different than DET2}
